---
title: "Clustering Analysis"
output:
  html_document: default
  html_notebook: default
---

#Date: "June 5 2017"



# Clustering Analysis in Cardinal

This analysis was preformed using a dataset without slide background information and done with a datamatrix of 2508 Peaks by 20920 Pixels. The tissue, sox and mox channels were determined through microscopy techniques and dimenions were reduced to match the maldi-msi dataset (done by Benedikt). Please see data processing and peak picking scripts to see how data dimensions were reduced. See data clustering script to determine how clusters were generated.

Set up working space

```{r}
rm(list=ls())
library(Cardinal)
library(ggplot2)
library(reshape2)
library(vegan)
library(ggdendro)
load('../Results/cluster-analysis-final.RData') ##ssc clustering 
load('../Results/Cardinal_Processed_Data.RData')
```

### Shrunken Centriods Clustering 

From the cardinal workflows document: 

"The spatial shrunken centroids clustering method for statistical analysis we introduce in Cardinal in the spatialShrunkenCentroids method. 

The Gaussian and adaptive weights are retained from the spatially-aware k-means clustering [3]. In addition, we introduce statistical regularization as in nearest shrunken centroids to enforce feature sparsity [4]. This means doing feature selection, so that the analysis automatically identifies informative m/z values."


```{r}
plot(summary(ssc.a))
summary(ssc.a)
```

We want to keep the shrinkage parameter as low as possible with getting the "best"" number of clusters

```{r}
mycol<-c('deeppink', 'mediumslateblue','lightblue','coral4','darkslategray','olivedrab3','mediumseagreen','darkgoldenrod','gray25','mediumblue',rep('gray',10))


mod<-list(r=2, k=15, s=12) ## Choose a model -- 10 groups, 124 features 
image(ssc.a, model=mod, col=mycol,strip=F)
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
summaryPlots <- function(dataset, results, model, segment, name, col) {
image(results, model = model, key = FALSE, column = segment, main = name,
layout = c(3, 2), col = col)
plot(results, model = model, key = FALSE, column = segment, mode = "centers",
main = "Shrunken mean spectrum", col = col)
plot(results, model = model, key = FALSE, column = segment, mode = "tstatistics",
main = "Shrunken t-statistics", col = col)
top <- topLabels(results, n = 3, model = model, filter = list(classes = segment))
image(dataset, mz = top$mz, contrast.enhance = "histogram")
 }
```

Plot each cluster group independently and choose top three ions that are part of that cluster
 
```{r}
pdf('Cluster-Distribution-Plots.pdf', height=6, width=11)
 for (i in 1:10){
   summaryPlots(maldifishmz,ssc.a,model=mod,segment=i, name='', col=mycol)
 }
dev.off()
```

Plot percentage of FISH signals in entire dataset across clusters. This will show us which clusters the percentange of the fish groups falls

% of FISH signals across clusters 


```{r}
## Specify same dataset used in cluter analysis
maldifishmz_3grps<-maldifishmz[,maldifishmz$Class %in% c('Tissue','Red','Green')]

## Get pixel data 
pDf<-data.frame(pData(maldifishmz_3grps))
pDf$rowname<-rownames(pDf)

## Get cluster data plus coordinates
cDf<-data.frame(Cluster=ssc.a$classes$`r = 2, k = 15, s = 12`)
cDf$rowname<-rownames(cDf)

## merge cluster annotations and pixel data
df.m<-merge(pDf, cDf, by = 'rowname')

## Call all Red and Green annotations symbionts
df.m[df.m$Class %in% c('Red','Green'),'Class']<-'Symbiont'

## Class membership across clusters
tab<-table(df.m$Class , df.m$Cluster)
total<-rowSums(tab)
tab<-data.frame(tab)
tab$Total<-total
tab$percent_of_group<-tab$Freq/total*100
tab<-tab[!tab$Freq==0,]

ggplot(tab, aes(x=as.factor(Var2), y=percent_of_group, fill=Var1)) + geom_bar(stat='identity', position='dodge')+ scale_fill_manual(values=c('gray80','black')) + ggtitle('% of all symbiont or host tissue identification signals across clusters') + ylab('% of  "FISH" Group') + xlab('Cluster Group') + guides(fill=guide_legend(title='FISH signal')) + theme_bw()
ggsave('../Results/Cluster Membership.eps')
```


Write a datatable for the significant ions across clusters

```{r}
tL<-topLabels(ssc.a, model=mod, n=10000) # just set a really high number
tL.sig<-tL[which(tL$adj.p.values < 0.2),]
dim(tL.sig)
table(tL.sig$classes)
write.csv(tL.sig, file='../Results/ssc-ions-clusterassignment.csv')
```


One thing interesting, there doens't seem to be any ions seperating cluster 8 from the other clusters. 

```{r}
table(ssc.a$classes$`r = 2, k = 15, s = 12`)
```

Not that many pixels in cluster 8


Make similar % cluster identity barplot for ions that are  of interest (i.e., significnat in seperating the groups)

```{r}
## select signficant ions  
#tmp<-maldifishmz_3grps[mz(maldifishmz_3grps) %in% unique(tL.sig$mz),]
tmp<-maldifishmz_3grps

## Write out dataframe & add in class info
mat<-spectra(tmp[,])
rownames(mat)<-tmp@imageData@dimnames[[1]] ## gets rownames
colnames(mat)<-tmp@imageData@dimnames[[2]]
df.tmp<-as.data.frame(t(mat))
df<-data.frame(Class=as.vector(tmp$Class),df.tmp)
df$Class<-as.vector(df$Class)

## Call all symbionts, symbionts
#df[df$Class %in% c('Red','Green'),'Class']<-'Symbiont'
ttls<-table(df$Class) ## totals

## Create vector of significnat ions
sigIons<-colnames(df[,grep('m.z',colnames(df))])

## make a new dataframe
okfor(i in 1:length(sigIons)){
ind<-sigIons[i] ## select ion
df.tmp<-data.frame(Class=df[,1],ion=df[,ind]) # create temp dataframe with ion of interest and fish calls
rng<-range(df.tmp$ion)
df.tmp<-df.tmp[df.tmp$ion > 0, ] # selects only pixels with values greater then 0
prct<-table(df.tmp$Class)/ttls ## calculates percent of pixels with a positive m/z value in terms of group totals 
prct_of_sgnls<-rbind(prct_of_sgnls,data.frame(mz=ind, sox_prct=as.vector(prct[1]), mox_prct=as.vector(prct[2]),host_prct=as.vector(prct[3]))) ## makes a handy dataframe
}

#prct_of_sgnls$diff<-abs(prct_of_sgnls$symbiont_prct - prct_of_sgnls$host_prct)
#prct_of_sgnls<-prct_of_sgnls[order(prct_of_sgnls$diff, decreasing = T),]


pdf('ion differences')
cols<-colorRampPalette(c('black','blue','lightblue'))
par(mfrow=c(1,2))
mzval<-482.361
image(maldifishmz_3grps,mz=mzval, col.regions=cols(50))
temp<-prct_of_sgnls[grep(mzval,prct_of_sgnls$mz),2:4]
vec<-as.matrix(temp)
barplot(height=vec, main='% of FISHed cells with ion intensity > 0 ')


cols<-colorRampPalette(c('black','blue','lightblue'))
par(mfrow=c(1,2))
mzval<-546.489 # hopanoid
image(maldifishmz_3grps,mz=mzval, col.regions=cols(50))
temp<-prct_of_sgnls[grep(mzval,prct_of_sgnls$mz),2:4]
vec<-as.matrix(temp)
barplot(height=vec, main='% of FISHed cells with ion intensity > 0 ')


mzval<-562.483
par(mfrow=c(1,2))
image(maldifishmz_3grps,mz=mzval, col.regions=cols(50))
temp<-prct_of_sgnls[grep(mzval,prct_of_sgnls$mz),2:4]
vec<-as.matrix(temp)
barplot(height=vec, main='% of FISHed cells with ion intensity > 0 ')


mzval<-732.554
par(mfrow=c(1,2))
cols<-colorRampPalette(c('black','blue','lightblue'))
image(maldifishmz_3grps,mz=mzval, col.regions=cols(50))
temp<-prct_of_sgnls[grep(mzval,prct_of_sgnls$mz),2:4]
vec<-as.matrix(temp)
barplot(height=vec, main='% of FISHed cells with ion intensity > 0 ')


mzval<-773.23
par(mfrow=c(1,2))
cols<-colorRampPalette(c('black','blue','lightblue'))
image(maldifishmz_3grps,mz=mzval, col.regions=cols(50))
temp<-prct_of_sgnls[grep(mzval,prct_of_sgnls$mz),2:4]
vec<-as.matrix(temp)
barplot(height=vec, main='% of FISHed cells with ion intensity > 0 ')


mzval<-756.554
par(mfrow=c(1,2))
cols<-colorRampPalette(c('black','blue','lightblue'))
image(maldifishmz_3grps,mz=mzval, col.regions=cols(50))
temp<-prct_of_sgnls[grep(mzval,prct_of_sgnls$mz),2:4]
vec<-as.matrix(temp)
barplot(height=vec, main='% of FISHed cells with ion intensity > 0 ')

dev.off()

```






#### Dendrogram of cluster groups
ta
```{r}
modResults<-ssc.a@resultData$`r = 2, k = 15, s = 12`

## Dataset that went into cluster analysis
maldifishmz_3grps<-maldifishmz[,maldifishmz$Class %in% c('Tissue','Red','Green')]

## Add in cluster group to spectra information 
maldifishmz_3grps$SSCA_Clusters_pixeln<-names(modResults$classes)
maldifishmz_3grps$SSCA_Clusters<-paste('ssca_cluster',modResults$classes,sep='-')


## Get mean spectra for each group
mean.sp<-data.frame(featureApply(maldifishmz_3grps, mean, .pixel.groups=maldifishmz_3grps$SSCA_Clusters))
mean.sp[,1:10]
mshapiro.test(U = as.matrix(mean.sp))

## Run hclust 
par(mfrow=c(2,2))
d<-vegdist(mean.sp,method = 'euclidean')
clusters<-hclust(d, method='average')
plot(clusters, main='euclidean')

d<-vegdist(mean.sp,method = 'bray')
clusters<-hclust(d, method='average')
plot(clusters,main='bray')

d<-vegdist(mean.sp,method = 'mahalanobis')
clusters<-hclust(d, method='average')
plot(clusters,main='mahalanobis')

d<-vegdist(mean.sp,method = 'manhattan')
clusters<-hclust(d, method='average')
plot(clusters,main='manhattan')


## Use manhattan differences 
d<-vegdist(mean.sp,method = 'manhattan')
clusters<-hclust(d, method='average')
plot(clusters,main='manhattan')

```


Make a nice plot for a figure
```{r}
dhc <- as.dendrogram(clusters)
ddata <- dendro_data(dhc, type = "rectangle",)
ddata$labels$label<-as.numeric(gsub('ssca_cluster-',' ',ddata$labels$label))
ddata$labels<-ddata$labels[order(ddata$labels$label),]

ggplot() + geom_segment(data = ddata$segments, aes(x = x, y = y, xend = xend, yend = yend)) + 
            geom_text(data = ddata$labels, aes(x = x, y = y, label = label, size = 3, vjust = 0.5, hjust=-0.5)) + 
            geom_point(data=label(ddata), aes(x=x, y=y, color=as.factor(label),size=3),shape=15) + 
            theme_dendro() + scale_y_reverse() + coord_flip() + scale_color_manual(values=mycol)  + guides(color=F, size=F) 

```





### Supervised Shrunken Centriods Clustering 

Creat a cross valiadation group
```{r}
maldifishmz$cvgroup<-cut(maldifishmz$y, breaks=5, labels = F) #based on y-location value in dataset
```


Add in cilliated edge pixels 

```{r}
grps<-ssc.a$classes$`r = 2, k = 15, s = 12`
ciliatedgrps<-grps[which(grps==2)]
grp1<-names(ciliatedgrps)
msidata<-maldifishmz
pData(msidata)[rownames(pData(msidata)) %in% grp1,'Class']<-'CiliatedEdge'
table(msidata$Class, msidata$cvgroup)
```

Run spatial shrunken centriods supervised clustering using the adaptive method and the associated parameters

```{r, message=FALSE, warning=FALSE, include=FALSE}
ssca.cv<-cvApply(msidata, .y=msidata$Class, .fun="spatialShrunkenCentroids",method='adaptive', .fold=cvgroup, r=c(1,2,3),s=c(0,1,3,6,12,24))
plot(summary(ssca.cv))
```

```{r}
ssca<-spatialShrunkenCentroids(x=msidata, y=msidata$Class, s=0, r=3)
summary(ssca)
ssca
plot(ssca, mode='tstatistics')
```
```{r}
image(ssca, model=list(r=3, s=0), col=c('midnightblue','mediumseagreen','lightcoral','skyblue'))
```


```{r}
tp<-topLabels(ssca, n=20000)
dim(tp)
table(tp$classes)
tp.sig<-tp[which(tp$adj.p.values < 0.2),]
write.csv(tp.sig,file='../Results/ssc-classification-sigions.csv')
```



