---
title: "Cluster Anlaysis"
output:
  html_document: default
  html_notebook: default
---

Set up working space

This data was only given information for host, sox and mox channels in supervised method.
```{r}
rm(list=ls())
library(Cardinal)
library(ggplot2)
library(reshape2)
load('../Results/ssc-adaptive-unsupervised-clustering-analysis.RData') ##ssc clustering 
load('../Results/unsupervised-clustering-analysis.RData') ## unsupervised clustering
load('../Results/supervised-clustering-anlaysis.RData')
ls()
```



## Unsupervised Clustering Analysis with Cardinal 

This is k-means spatial clustering, we told the program to find clusters at k=3,5, & 7 with smoothing radius at 1 & 2. This is for a visual representation of the data. Please see the SCC for statistical support of the cluster groups

```{r}
print('adaptive')
summary(skma)
image(skma, key = T, layout = c(3, 2))
```


```{r}
print('gaussian')
summary(skmg)
image(skmg, key = T, layout = c(3, 2))
```

Both the gaussian and adaptive methods give similar results. The heterogenius tissue likely requires a smoothing radius of 1 because of the patchyness. Suggest using only the adaptive weights moving forward in the analysis. 


#### Spatial shrunken centrioids clustering to provide segmentation graphics

From the cardinal workflows document: 

"The spatial shrunken centroids clustering method for statistical analysis we introduce in Cardinal in the spatialShrunkenCentroids method. 

The Gaussian and adaptive weights are retained from the spatially-aware k-means clustering [3]. In addition, we introduce statistical regularization as in nearest shrunken centroids to enforce feature sparsity [4]. This means doing feature selection, so that the analysis automatically identifies informative m/z values."

```{r}
print('Adaptive')
summary(ssc.a)
```

Plot the spatial segments 

```{r}
plot(summary(ssc.a))
```

From this analysis, there seems to be a lot of variation in the data, but every time I run it (which takes ~12 hrs to run), we are coming up with s=15, k=15 or 20 and r=1 or 2 as converging on the same number of preditive classes (8)

use model: r=2, k=15, s=15 for subsequent investigations 


```{r}
mycol<-c('midnightblue', 'mediumturquoise','dodgerblue', 'firebrick1','gold','seagreen4', 'plum', 'mediumvioletred', 'indianred4', 'hotpink', 'darkslategray1', 'forestgreen','olivedrab1', 'skyblue','dodgerblue4','mediumspringgreen','coral1', 'cyan','azure','cadetblue4')
image(ssc.a, model=list(r=2,k=20, s=9), col=mycol)
```


```{r, message=FALSE, warning=FALSE, include=FALSE}
summaryPlots <- function(dataset, results, model, segment, name, col) {
image(results, model = model, key = FALSE, column = segment, main = name,
layout = c(3, 2), col = col)
plot(results, model = model, key = FALSE, column = segment, mode = "centers",
main = "Shrunken mean spectrum", col = col)
plot(results, model = model, key = FALSE, column = segment, mode = "tstatistics",
main = "Shrunken t-statistics", col = col)
top <- topLabels(results, n = 3, model = model, filter = list(classes = segment))
image(dataset, mz = top$mz, contrast.enhance = "histogram")
 }
```


Summerize important segments through plots

```{r}
load('../Data/Cardinal_Processed_Data.RData')
```


```{r}
summaryPlots(maldifishmz,ssc.a,model=list(r=2,k=20, s=9),segment=1, name='matrix scatter', col=mycol)
summaryPlots(maldifishmz,ssc.a,model=list(r=2,k=20, s=9),segment=2, name='Cilated Edge', col=mycol)
summaryPlots(maldifishmz,ssc.a,model=list(r=2,k=20, s=9),segment=3, name=' Bacteria rich region', col=mycol)
summaryPlots(maldifishmz,ssc.a,model=list(r=2,k=20, s=9),segment=4, name='Matrix Scatter', col=mycol)
summaryPlots(maldifishmz,ssc.a,model=list(r=2,k=20, s=9),segment=5, name='Bacterial rich region', col=mycol)
summaryPlots(maldifishmz,ssc.a,model=list(r=2,k=20, s=9),segment=6, name='noise', col=mycol)
summaryPlots(maldifishmz,ssc.a,model=list(r=2,k=20, s=9),segment=7, name='Ciliated Edge', col=mycol)
summaryPlots(maldifishmz,ssc.a,model=list(r=2,k=20, s=9),segment=8, name='Bacterial rich region', col=mycol)
summaryPlots(maldifishmz,ssc.a,model=list(r=2,k=20, s=9),segment=9, name='Ciliated Edge', col=mycol)
```




```{r}
## Get pixel data 
pDf<-data.frame(pData(maldifishmz))
pDf$rowname<-rownames(pDf)

## Get cluster data plus coordinates
cDf<-data.frame(Cluster=ssc.a$classes$`r = 2, k = 20, s = 15`)
cDf$rowname<-rownames(cDf)

## merge cluster annotations and pixel data
df.m<-merge(pDf, cDf, by = 'rowname')

## Class membership across clusters
tab<-table(df.m$Class , df.m$Cluster)
total<-rowSums(tab)
tab<-data.frame(tab)
tab$Total<-total
tab$percent_of_group<-tab$Freq/total*100
tab<-tab[!tab$Freq==0,]

ggplot(tab, aes(x=as.factor(Var2), y=Freq, fill=Var1)) + geom_bar(stat='identity', position='dodge')+ scale_fill_manual(values=c('mediumseagreen','lightcoral','skyblue')) + ggtitle('Frequence of FISH Assignments across clusters') + ylab('Frequency of FISH calles') + xlab('Cluster Group')

ggplot(tab, aes(x=as.factor(Var1), y=percent_of_group, fill=Var2)) + geom_bar(stat='identity')+ scale_fill_manual(values=mycol) + ggtitle('FISH Category Cluster Membership') + ylab('Percent of "FISH" Group') + xlab('FISH Category') + guides(fill=guide_legend(title='Cluster Group'))

ggplot(tab, aes(x=as.factor(Var2), y=percent_of_group, fill=Var1)) + geom_bar(stat='identity', position='dodge')+ scale_fill_manual(values=c('mediumseagreen','lightcoral','skyblue')) + ggtitle('Percent of group membership across clusters') + ylab('Percent of "FISH" Group') + xlab('FISH Category') + guides(fill=guide_legend(title='FISH Group'))
```



## Supervised Clustering Analysis with Cardinal 

The analysis below is a supervised clustering analysis, where we told Cardinal that we expect to have 3 groups (host, mox, sox) and to find signals that are related to these groups using a cross valudation method. The data was randomly split into 8 CV groups and the analysis was preformed by leaving out the signals from one group at a time. This was done for both the adaptive method and the gaussian method. 

```{r}
plot(summary(ssca.cv))
```



```{r}
image(ssca.cv, model = list(r = 3, s = 0), layout = c(3,2))
```
Now re-run on full dataset with parameters, r=3, s=0

```{r}
ssca.msi<-spatialShrunkenCentroids(msidata, y = msidata$Class, r = 3,s = 0, method = "adaptive")
summary(ssca.msi)
```

```{r}
topLabels(ssca.msi,  n=100)
```


```{r}
mycols2<-c('midnightblue','mediumseagreen','lightcoral','skyblue')
image(ssca.msi, model = list(r = 3, s = 0), col=mycols2)
```

Predictive model components for spatial clustering analysis 


```{r}
topIons <- function(dataset, results, segment) {
top <- topLabels(results, n = 3, filter = list(classes = segment))
image(dataset, mz = top$mz, normalize.image = "linear", contrast.enhance = "histogram",
smooth.image = "gaussian", main=segment)
}
```



```{r}
topIons(msidata, ssca.msi, segment='CiliatedEdge')
topIons(msidata, ssca.msi, segment='Red')
topIons(msidata, ssca.msi, segment='Green')
topIons(msidata, ssca.msi, segment='Tissue')
```

```{r}
plot(ssca.msi, mode = "tstatistics", col=mycols2)
```





