---
title: "Exploring maldifish data"
output:
  html_document: default
  html_notebook: default
---

set up working space

```{r, message=FALSE, warning=FALSE}
rm(list=ls())
library(Cardinal)
library(VennDiagram)
library(ggplot2)
library(gplots)
library(gridExtra)
load('../Data/Cardinal_Processed_Data_June2017.RData')
```


# Fish binning of metabolomes


```{r}
table(int_matrix$Class)
```

Need to create lists of peaks that are in each channel. To be considered in channel, the mz value must of a mean intensity across the group of at least 10 
This threshold should be considered throughoughly 

```{r}
trsh=10

# Tissue
channel<-'Host'
df<-int_matrix[which(int_matrix$Class==channel),]
mz.means<-colMeans(df[,sapply(df,is.numeric)])
summary(mz.means)
Tissue<-names(mz.means[which(mz.means > trsh)])
tsh<-mz.means[which(mz.means > trsh)]

# Mox
channel<-'Mox'
df<-int_matrix[which(int_matrix$Class==channel),]
mz.means<-colMeans(df[,sapply(df,is.numeric)])
summary(mz.means)
Mox<-names(mz.means[which(mz.means > trsh)])

# Sox
channel<-'Sox'
df<-int_matrix[which(int_matrix$Class==channel),]
mz.means<-colMeans(df[,sapply(df,is.numeric)])
summary(mz.means)
Sox<-names(mz.means[which(mz.means > trsh)])

chns<-list(Tissue, Mox, Sox)
```


```{r}
par(mfrow=c(2,3))
#pdf('../Results/intensityBinning.pdf', width=10, height=10)
tsh<-tsh[order(tsh)]
image(maldifishmz,mz=c('501.487'), main='Mean Intensity=10')
image(maldifishmz,mz=c('1010.089'), main='Mean Intensity=25')
image(maldifishmz,mz=c('894.583 '), main='Mean Intensity=40')
image(maldifishmz,mz=c('897.604 '), main='Mean Intensity=80')
image(maldifishmz,mz=c('600.031 '), main='Mean Intensity=100')
image(maldifishmz,mz=c('528.307 '), main='Mean Intensity=500')
#dev.off()

plot(maldifishmz, pixel=1:ncol(maldifishmz), pixel.groups=maldifishmz$Class, superpose=T, key=T, col=c('skyblue', 'lightcoral','mediumseagreen'))

```


Compare through venn-diagrams

```{r}
venn.diagram(x = chns, category.names = c('Host','Mox','Sox'),filename = '../Results/FishBinned_Metabolome.eps', fill=c('skyblue', 'lightcoral','mediumseagreen'))
venn<-venn.diagram(x = chns, category.names = c('Host','Mox','Sox'),filename = NULL, fill=c('skyblue', 'lightcoral','mediumseagreen'))
grid.arrange(gTree(children=venn), ncol=1,newpage = T)
```

Determine which features are unique between channels 

```{r}
metlist<-chns
names(metlist)<-c('Tissue', 'Mox', 'Sox')
a<-venn(metlist, show.plot=F)
inters <- attr(a,"intersections")
m<-data.frame(mz=inters$Mox, label='mox')
s<-data.frame(mz=inters$Sox, label='sox')
h<-data.frame(mz=inters$Tissue, label='host')
c<-data.frame(mz=inters$`Tissue:Mox:Sox`, label='common')
vlists<-rbind(m,s,h,c)
write.csv(vlists, file='../Results/VennDiagram-Seperated-Ion-List.csv')
```

# PCA Analysis

Runs a PCA model on entire dataset with 4 components 
```{r}
set.seed(seed = 1)
pca.mod<-PCA(maldifishmz,ncomp=2)
summary(pca.mod)
plot(summary(pca.mod))
```


Visualize PCA analysis 

```{r}
mycols<-gradient.colors(10,start='royalblue', end='goldenrod')
#postscript('../Results/PCA.eps', height=12, width=18)
par(mfrow=c(1,2))
image(pca.mod, column=c('PC1','PC2'), superpose=F, col.regions=mycols)
#dev.off()
```


We can see clear seperation in the data based on PC components 1 and 2. Plot in scatter plot and color according to class category

```{r}
## Set up data for plotting
pca.scores.red<-as.data.frame(pca.mod[[1]]$scores[maldifishmz$Class=='Mox',])
pca.scores.red$Class<-'mox'

pca.scores.green<-as.data.frame(pca.mod[[1]]$scores[maldifishmz$Class=='Sox',])
pca.scores.green$Class<-'sox'

pca.scores.tissue<-as.data.frame(pca.mod[[1]]$scores[maldifishmz$Class=='Host',])
pca.scores.tissue$Class<-'host'

pca.scores<-rbind(pca.scores.green,pca.scores.red,pca.scores.tissue)
pca.scores.symbionts<-pca.scores[pca.scores$Class %in% c('mox','sox'),]

ggplot(pca.scores, aes(x=PC1, y=PC2, color=Class)) + geom_point() + geom_point(data=pca.scores.symbionts,aes( x=PC1, y=PC2, color=Class)) + theme_bw() + scale_color_manual(values=c('skyblue', 'lightcoral','mediumseagreen'))
ggsave('../Results/PCA_scatter.eps')
```


The ciliated edge of the tissue regions looks to be metabolically different from the rest of the tissue sections. This is also supported from the clustering results presented in the Cluster analysis notebook.


<<<<<<< HEAD
## Testing For Correlations bewteen FISH-Intensity and Metabolites 

```{r}
red<-read.table('../Data/RedCh_Intensity_1-255_xycoord_233x233pix.txt')
colnames(red)<-c('X','Y','MoxInt')

range(red$MoxInt)
red$XY<-paste('x = ',red$X, ', y = ', red$Y, sep='')

newMat<-data.frame(XY=rownames(int_matrix),int_matrix)
newMat.merge<-merge(red, newMat, by='XY')
newMat.merge<-newMat.merge[order(newMat.merge$MoxInt),]

#546.4886
hop1<-newMat.merge$m.z...546.489
moxInt<-newMat.merge$MoxInt

hops<-data.frame(moxInt=newMat.merge$MoxInt, hop1=newMat.merge$m.z...546.489, hop2=newMat.merge$m.z...547.473, hop3=newMat.merge$m.z...562.483, CEMet=newMat.merge$m.z...482.361, hops4=newMat.merge$m.z...546.489)

plot(hops$moxInt, hops$hops4)


plot(hops$hop1, hops$hop2)
plot(hops$hop2, hops$hop3)
pairs(hops)


hops.nozs<-hops[-which(hops$moxInt < 50),]
pairs(hops.nozs)
plot(hops.nozs$moxInt, hops.nozs$hop1)


plot(hops$moxInt, hops$CEMet)

cors<-rcorr(x = hops$moxInt, y=hops$hops4, type='spearman')
cors$r
cors$P

plot(hops$moxInt, hops$hops4, main='Correlation (spearman rank) r= 0.2, p < 0.05', xlab='Mox Int Value', ylab='Relative Int of m.z 546.489')
```


=======
# Some more peak exploration 

From previous experiments, we know that the mox signals should be linked to the hopanoids

```{r}
hops<-data.frame(Class=int_matrix$Class, hop1=int_matrix$m.z...546.489, hop2=int_matrix$m.z...546.526, hop3=int_matrix$m.z...562.483, ce=int_matrix$m.z...756.554)

table(hops[hops$hop1 > 500,'Class'])/table(int_matrix$Class)
table(hops[hops$ce > 500,'Class'])/table(int_matrix$Class)

image(maldifishmz,mz=756.554)
image(maldifishmz,mz=546.489)
image(maldifishmz,mz=546.526)

mod<-aov(hops$hop1 ~ hops$Class)
summary(mod)
plot(mod)

meanHop1<-aggregate(hops$hop1 ~ hops$Class, FUN=mean)
mh1<-as.vector(meanHop1$`hops$hop1`)
class<-meanHop1$`hops$Class`
barplot(height = mh1 , names.arg = class)


meanHop2<-aggregate(hops$hop2 ~ hops$Class, FUN=mean)
mh2<-as.vector(meanHop2$`hops$hop2`)
class<-meanHop2$`hops$Class`
barplot(height = mh2 , names.arg = class)


meanhop3<-aggregate(hops$hop3 ~ hops$Class, FUN=mean)
mh3<-as.vector(meanhop3$`hops$hop3`)
class<-meanhop3$`hops$Class`
barplot(height = mh3 , names.arg = class)

meanCE<-aggregate(hops$ce ~ hops$Class, FUN=mean)
mce<-as.vector(meanCE$`hops$ce`)
class<-meanCE$`hops$Class`
barplot(height = mce , names.arg = class)

```


```{r}
head(int_matrix[,1:10])
rmat<-data.frame(Class=int_matrix$Class, PC1=int_matrix$m.z...756.554, PC2=int_matrix$m.z...732.554, 
                 Methan=int_matrix$m.z...773.24, hop=int_matrix$m.z...546.489)
tots<-table(rmat$Class)
mets<-colnames(rmat)[-1]

prct_of_sgnls<-data.frame()
for(i in 1:length(mets)){
ind<-mets[i] ## select ion
df.tmp<-data.frame(Class=rmat[,1],ion=rmat[,ind]) # create temp dataframe with ion of interest and fish calls
rng<-range(df.tmp$ion)
df.tmp<-df.tmp[df.tmp$ion > rng[2]*.1, ] # selects only pixels with values greater then 0
prct<-table(df.tmp$Class)/tots ## calculates percent of pixels with a positive m/z value in terms of group totals 
prct_of_sgnls<-rbind(prct_of_sgnls,data.frame(mz=ind, sox_prct=as.vector(prct[4]), mox_prct=as.vector(prct[3]),host_prct=as.vector(prct[1]))) ## makes a handy dataframe
}
prct_of_sgnls

```


## More Exploration with PCA

```{r}
mox_int<-int_matrix[int_matrix$Class=='Mox',]
mpca<-prcomp(mox_int[,2:ncol(mox_int)], scale=T, center=T)
scores<-data.frame(mpca$x[,1:3])
plot(scores)

scores$rn<-as.vector(rownames(scores))
mox_int$rn<-as.vector(rownames(mox_int))

## merge hopanoid value with PC scores
mox_hop<-data.frame(rn=mox_int$rn, hop1=mox_int$m.z...546.489, ce=mox_int$m.z...756.554)
sc.m<-merge(scores, mox_hop, by= 'rn')

ggplot(sc.m, aes(x=PC1, y=PC2, color=hop1)) + geom_point() + scale_fill_gradient(limits=c(0,51000)) + scale_x_continuous(limits=c(-30,70)) + scale_y_continuous(limits=c(-30,50))

x<-sc.m[sc.m$hop1 > 0, ]
ggplot(x,aes(x=PC1, y=PC2, color=hop1)) + geom_point()  + scale_fill_gradient(limits=c(0,51000)) + scale_x_continuous(limits=c(-30,70)) + scale_y_continuous(limits=c(-30,50))

x<-sc.m[sc.m$hop1 > 1000, ]
ggplot(x,aes(x=PC1, y=PC2, color=hop1)) + geom_point() +  scale_fill_gradient(limits=c(0,51000)) + scale_x_continuous(limits=c(-30,70)) + scale_y_continuous(limits=c(-30,50))


x<-sc.m[sc.m$hop1 > 5000, ] # 10% of max
ggplot(x,aes(x=PC1, y=PC2, color=hop1)) + geom_point()+ scale_fill_gradient(limits=c(0,51000)) + scale_x_continuous(limits=c(-30,70)) + scale_y_continuous(limits=c(-30,50))


ggplot(sc.m, aes(x=PC1, y=PC2, color=ce)) + geom_point() + scale_fill_gradient(limits=c(0,8000)) + scale_x_continuous(limits=c(-30,70)) + scale_y_continuous(limits=c(-30,50))

x<-sc.m[sc.m$ce > 0, ]
ggplot(x,aes(x=PC1, y=PC2, color=ce)) + geom_point()  + scale_fill_gradient(limits=c(0,8000)) + scale_x_continuous(limits=c(-30,70)) + scale_y_continuous(limits=c(-30,50))

x<-sc.m[sc.m$ce > 100, ]
ggplot(x,aes(x=PC1, y=PC2, color=ce)) + geom_point() +  scale_fill_gradient(limits=c(0,8000)) + scale_x_continuous(limits=c(-30,70)) + scale_y_continuous(limits=c(-30,50))

x<-sc.m[sc.m$ce > 600, ] # 10% of max
ggplot(x,aes(x=PC1, y=PC2, color=ce)) + geom_point()+ scale_fill_gradient(limits=c(0,8000)) + scale_x_continuous(limits=c(-30,70)) + scale_y_continuous(limits=c(-30,50))
```


Heat map of mox signals 

```{r}
x<-as.matrix(mox_int[,grep('m.z.', colnames(mox_int))]
heatmap.2(x)
```



>>>>>>> 62198749dfbdf8e7c87e817c8eb4a3bd7ee9550e



### END Analysis 


