---
title: "ClassificationAnalysis"
output: html_notebook
---

Set up working space

```{r, warning=FALSE}
rm(list=ls())
library(Cardinal)
load('../Data/Cardinal_Processed_Data.RData')
```


From our exploratory analysis & clustering results, we know that we have another tissue category group called "cillated edge", for this analysis it is essential to provide an additional category to our class vector that denotes if a tissue group is the cilated edge. 

Grab the clustering results data
```{r}
load('../Results/HostSoxMox/unsupervised-clustering-analysis.RData') ## unsupervised clustering
image(skma, key = T, model=list(r=2, k=7))
grps<-skma$cluster$`r = 2, k = 7`
ciliatedgrps<-grps[which(grps==1)]
grp1<-names(ciliatedgrps)

msidata<-maldifishmz
pData(msidata)[rownames(pData(msidata)) %in% grp1,'Class']<-'CiliatedEdge'
```

As a sanity check, make an msi data object without the cilated edge and use PCA to visualize vairation in data without this region 
```{r}
msidata.nce<-msidata[,msidata$Class %in% c('Red','Green','Tissue')] ## selects only for the red, green, tissue calls
pca.nce<-PCA(msidata.nce,ncomp=2) ## preforms pca with 3 components
plot(summary(pca.nce)) ## gives broken stick model
image(pca.nce, column=c('PC1','PC2'), superpose=T) # plots PC scores across image
```

Need to make a cross validation group for all data by splitting along the Y axis 
```{r}
## Assign cross validation groups based on y-axis coordinates --> basically each filiament(?) will be it's own CV group more or less 
msidata$CV<-cut(msidata$y, breaks=8, labels = F) # Lets stick with 10 CV groups

## Visualize a few of the cuts (CV groups)
msi1<-msidata[,msidata$CV %in% c(3,5,7)]
pca.msi1<-PCA(msi1, ncomp=2)
image(pca.msi1, superpose=T)
```

# Classification Analysis 
The parameters from the models below are calculated from a portion of the data and compared across all models generated for each cross validation group. 

These models are typically biased by varying group sizes. This can be solved by evening out the groups as below: 

```{r}
msidata<-msidata[,!msidata$Class %in% c('Mixed')] ## remve mixed category 
table(msidata$Class, msidata$CV)

temp<-data.frame(pData(msidata)) ## get pixel data out from object
temp$xy<-paste(temp$x, temp$y,sep='-') ## get xy values to help insubsetting

set.seed(1) #Always start in the same place
subset<-data.frame((pData(msidata) %>% group_by(Class) %>% sample_n(size=700,replace = F))) ## randomly select 700 pixels for each group
subset$xy<-paste(subset$x, subset$y,sep='-') # pixels select for anlaysis 

coords<-rownames(temp[temp$xy %in% subset$xy,]) ## gets the pixels to keep
msidata.subset<-msidata[,rownames(pData(msidata)) %in% coords] ## subsets data
table(msidata.subset$Class, msidata.subset$CV) ## number of pixels across cv folds
```

Some inbalances across the individual folds, but should be OK

### Full Model PLS Analysis 

```{r, message=FALSE, warning=FALSE}
set.seed(1)
pls.cv<-cvApply(msidata.subset, .y = as.factor(msidata.subset$Class), .fun = "PLS", ncomp = 1:40, keep.Xnew = FALSE, .fold=CV)
plot(summary(pls.cv))

```

```{r}
set.seed(1)
comp<-35
pls<-PLS(x=msidata.subset,y=as.factor(msidata.subset$Class), ncomp=comp)
summary(pls)
```

Visualize PCA Results 

```{r}
plot(pls,col=c('Purple','Green','Red','Cyan'))
image(pls, model=list(ncomp=comp), col=c('Purple','Green','Red','Cyan'))
```
The way to interpert this, is we can predict the ciliated edge quite well with the data, the other categorys we are between 30 and 30 % of the time wrong with our prediction. 

```{r}
scores<-data.frame(pls$scores)
colnames(scores)<-paste('Comp', 1:ncol(scores),sep='-')
classes<-as.vector(pls$y)
pls.scores<-data.frame(Classes=classes,scores)
colnames(pls.scores)[1]<-'Classes'

## Plot components 1 vs. the predictive component --35
ggplot(pls.scores, aes(x=Comp.1, y=Comp.35, color=Classes)) + geom_point() + xlab('Component 1') + ylab('Component 35') + scale_color_manual(values=c('Purple','Green','Red','Cyan'))

## plot component 1 vs. 2
ggplot(pls.scores, aes(x=Comp.1, y=Comp.2, color=Classes)) + geom_point() + xlab('Component 1') + ylab('Component 2') + scale_color_manual(values=c('Purple','Green','Red','Cyan'))
```

It is clear the cilated edge is distinct from the tissue, but to confirm we can also build an OPLS-DA model with just the cilaited edge nad tissue pixels incorperated


### Comparison between ciliated edge and tissue 

Run an OPLS-Da model to compare ciliated edge host tissue pixels vs. normal tissue pixels 

```{r}
msidata.subset
```



### Comparison between mox and host tissue 

Remove ciliated edge tissues 




