---
title: "Exploring maldifish data"
output:
  html_document: default
  html_notebook: default
---

set up working space

```{r, message=FALSE, warning=FALSE}
rm(list=ls())
library(Cardinal)
library(VennDiagram)
library(ggplot2)
library(gplots)
library(gridExtra)
load('../Results/Cardinal_Processed_Data.RData')
```


# Fish binning of metabolomes


```{r}
table(int_matrix$Class)
```

Need to create lists of peaks that are in each channel. To be considered in channel, the mz value must of a mean intensity across the group of at least 10 
This threshold should be considered throughoughly 

```{r}
trsh=10

# Tissue
channel<-'Tissue'
df<-int_matrix[which(int_matrix$Class==channel),]
mz.means<-colMeans(df[,sapply(df,is.numeric)])
summary(mz.means)
Tissue<-names(mz.means[which(mz.means > trsh)])
tsh<-mz.means[which(mz.means > trsh)]

# Mox
channel<-'Red'
df<-int_matrix[which(int_matrix$Class==channel),]
mz.means<-colMeans(df[,sapply(df,is.numeric)])
summary(mz.means)
Mox<-names(mz.means[which(mz.means > trsh)])

# Sox
channel<-'Green'
df<-int_matrix[which(int_matrix$Class==channel),]
mz.means<-colMeans(df[,sapply(df,is.numeric)])
summary(mz.means)
Sox<-names(mz.means[which(mz.means > trsh)])

chns<-list(Tissue, Mox, Sox)
```


```{r}
par(mfrow=c(2,3))
#pdf('../Results/intensityBinning.pdf', width=10, height=10)
tsh<-tsh[order(tsh)]
image(maldifishmz,mz=c('501.487'), main='Mean Intensity=10')
image(maldifishmz,mz=c('1010.089'), main='Mean Intensity=25')
image(maldifishmz,mz=c('894.583 '), main='Mean Intensity=40')
image(maldifishmz,mz=c('897.604 '), main='Mean Intensity=80')
image(maldifishmz,mz=c('600.031 '), main='Mean Intensity=100')
image(maldifishmz,mz=c('528.307 '), main='Mean Intensity=500')
#dev.off()

plot(maldifishmz, pixel=1:ncol(maldifishmz), pixel.groups=maldifishmz$Class, superpose=T, key=T, col=c('skyblue', 'lightcoral','mediumseagreen'))

```



Compare through venn-diagrams

```{r}
venn.diagram(x = chns, category.names = c('Host','Mox','Sox'),filename = '../Results/FishBinned_Metabolome.eps', fill=c('skyblue', 'lightcoral','mediumseagreen'))
venn<-venn.diagram(x = chns, category.names = c('Host','Mox','Sox'),filename = NULL, fill=c('skyblue', 'lightcoral','mediumseagreen'))
grid.arrange(gTree(children=venn), ncol=1,newpage = T)
```

Determine which features are unique between channels 

```{r}
metlist<-chns
names(metlist)<-c('Tissue', 'Mox', 'Sox')
a<-venn(metlist, show.plot=F)
inters <- attr(a,"intersections")
m<-data.frame(mz=inters$Mox, label='mox')
s<-data.frame(mz=inters$Sox, label='sox')
h<-data.frame(mz=inters$Tissue, label='host')
c<-data.frame(mz=inters$`Tissue:Mox:Sox`, label='common')
vlists<-rbind(m,s,h,c)
write.csv(vlists, file='../Results/VennDiagram-Seperated-Ion-List.csv')
```

# PCA Analysis

Runs a PCA model on entire dataset with 4 components 
```{r}
set.seed(seed = 1)
pca.mod<-PCA(maldifishmz,ncomp=2)
summary(pca.mod)
plot(summary(pca.mod))
```


Visualize PCA analysis 

```{r}
mycols<-gradient.colors(10,start='royalblue', end='goldenrod')
#postscript('../Results/PCA.eps', height=12, width=18)
par(mfrow=c(1,2))
image(pca.mod, column=c('PC1','PC2'), superpose=F, col.regions=mycols)
#dev.off()
```


We can see clear seperation in the data based on PC components 1 and 2. Plot in scatter plot and color according to class category

```{r}
## Set up data for plotting
pca.scores.red<-as.data.frame(pca.mod[[1]]$scores[maldifishmz$Class=='Red',])
pca.scores.red$Class<-'mox'

pca.scores.green<-as.data.frame(pca.mod[[1]]$scores[maldifishmz$Class=='Green',])
pca.scores.green$Class<-'sox'

pca.scores.tissue<-as.data.frame(pca.mod[[1]]$scores[maldifishmz$Class=='Tissue',])
pca.scores.tissue$Class<-'host'

pca.scores<-rbind(pca.scores.green,pca.scores.red,pca.scores.tissue)
pca.scores.symbionts<-pca.scores[pca.scores$Class %in% c('mox','sox'),]

ggplot(pca.scores, aes(x=PC1, y=PC2, color=Class)) + geom_point() + geom_point(data=pca.scores.symbionts,aes( x=PC1, y=PC2, color=Class)) + theme_bw() + scale_color_manual(values=c('skyblue', 'lightcoral','mediumseagreen'))
ggsave('../Results/PCA_scatter.eps')
```


The ciliated edge of the tissue regions looks to be metabolically different from the rest of the tissue sections. This is also supported from the clustering results presented in the Cluster analysis notebook.


## Testing For Correlations bewteen FISH-Intensity and Metabolites 

```{r}
red<-read.table('../Data/RedCh_Intensity_1-255_xycoord_233x233pix.txt')
colnames(red)<-c('X','Y','MoxInt')

range(red$MoxInt)
red$XY<-paste('x = ',red$X, ', y = ', red$Y, sep='')

newMat<-data.frame(XY=rownames(int_matrix),int_matrix)
newMat.merge<-merge(red, newMat, by='XY')
newMat.merge<-newMat.merge[order(newMat.merge$MoxInt),]

#546.4886
hop1<-newMat.merge$m.z...546.489
moxInt<-newMat.merge$MoxInt

hops<-data.frame(moxInt=newMat.merge$MoxInt, hop1=newMat.merge$m.z...546.489, hop2=newMat.merge$m.z...547.473, hop3=newMat.merge$m.z...562.483, CEMet=newMat.merge$m.z...482.361, hops4=newMat.merge$m.z...546.489)

plot(hops$moxInt, hops$hops4)


plot(hops$hop1, hops$hop2)
plot(hops$hop2, hops$hop3)
pairs(hops)


hops.nozs<-hops[-which(hops$moxInt < 50),]
pairs(hops.nozs)
plot(hops.nozs$moxInt, hops.nozs$hop1)


plot(hops$moxInt, hops$CEMet)

cors<-rcorr(x = hops$moxInt, y=hops$hops4, type='spearman')
cors$r
cors$P

plot(hops$moxInt, hops$hops4, main='Correlation (spearman rank) r= 0.2, p < 0.05', xlab='Mox Int Value', ylab='Relative Int of m.z 546.489')
```





### END Analysis 


